Large Scale Structure Reconstruction with Short-Wavelength Modes

### 2020-02-12 paper/response.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\newcommand\sd[1]{\emph{\bf [SD: #1]}}

\title{Response}
\author{Peikai Li, Scott Dodelson and Rupert A. C. Croft}
\date{}
\begin{document}

\maketitle
\noindent We sincerely thank the referees for their helpful comments and suggestions, which have significantly improved the manuscript.\\ \\
Following are the specific changes we have made:\\ \\
---------------------------------------------------------------------\\
Report of Referee A -- LK17288/Li\\
---------------------------------------------------------------------\\
\begin{itemize}
\item Referee's suggestion: \textbf{Although the paper shows solid analysis and demonstration with N-body
simulation and the method is relatively new, the small-scale
reconstruction has appeared in Physical Reviews in a couple of times:
for measuring gravitational waves (Masui \& Pen 2010, Jeong \&
Kamionkowski 2011, both PRL), for reconstructing the missing
long-wavelength mode for the 21cm surveys (Zhu, Pen+2015; 2016, both
PRD). All of the references mentioned above are missing in the paper.} \\ \\
Response: We cited all these papers.
\item Referee's suggestion: \textbf{In eq. (1)-(2), the authors use rather unconventional notation
$\times$ to represent the scalar product of two vectors.}
\\ \\Response: We fixed this error. 
\item Referee's suggestion: \textbf{Although the authors mention the 20\% bias on the right panel of Fig
2, showing summary statistics for the figure might be more helpful for
readers to understand the result.}
\\ \\Response: We also stated that the behavior of polar angle difference of the estimated and directly measured modes is worse in the second case. 
\item \textbf{There is a missing reference (shown as ??) on page 3.}\\ \\
Response: We fixed this error.\\

\end{itemize} 
---------------------------------------------------------------------\\
Report of Referee B -- LK17288/Li\\
---------------------------------------------------------------------\\

\begin{itemize}
\item Referee's suggestion: \textbf{First sentence is too long—split}
\\ \\Response: This is similar to the comment from Referee A; please see our response there.
\item Referee's suggestion: \textbf{\\Should have citations for upcoming surveys;\\ Overall I think much more connection to the literature on density reconstruction needs to be made. e.g. work by Jens Jasche, work by Uros Seljak, Florent Leclercq, etc. \\}
\\ \\Response: Cited LSST and WFIRST as upcoming surveys and the papers referee has recommended.
\item Referee's suggestion: \textbf{\\1. An large-scale -$>$ a large-scale;\\2. Second-order perturbation of -$>$ contribution to; \\3. Along line of sight -$>$ missing the; \\4. Calculate its detectability -$>$ assess; \\ 5. Large parens in equation 2 around lhs; \\ 6. Need to define everything in (1)-(3): missing Phi, rho\_m, a, tau; \\7. define the Dirac delta distribution in the text
Also define what $<>$ means;\\ 8. Large parens in equation 8 last term;\\ 9. Say in words what you have done in equation 11—take the low-k mode outside the
expectation value; \\
10. I think the little f function is necessary, just combine (13) and (14); \\ 11. Below (14), explain more: you mean that the lhs of (13) has only short modes, but the
rhs shows sensitivity to long modes; \\ 12. Signal-to-noise needs dashes;\\ 13. In equation (19), if you would not have used the f function, you would find that the factor of 2 cancels out. And the weight is more understandable written as
$[F2*P_{lin}(ks) + F2*P_{lin}(ks’)]/P_{nl}*P_{nl}]$ because it’s basically dividing out nonlinearities
and then rescaling by a particular estimate of the nonlinearity;\\ 14. Bottom left page 3: Fig ?? Missing number in text;\\ 15. formatting at top of page 3 is not good; 16. “Larger than the matter radiation equality”—missing dash. Clearer would be “than the scale entering the horizon at matter-radiation equality”; \\17. Fig 2 caption is not ideal—please actually state what this Figure shows in the caption; \\18. An exciting next step”—that seems subjective. I think you should just say “is the logical next step”.}
\\ \\Response: We have improved these expressions according to the suggestions here.
\item Referee's suggestion: \textbf{Dash in Fourier-transformed}
\\ \\Response: We don't think it is necessary in our case. First of all, we don't think it will cause much confusion. Secondly, the definition of the quadratic estimator ( Eq(15) ) already had a hat on it. We feel that it will be redundant for it to have both "hat" and "dash".
\item Referee's suggestion: \textbf{“Completely accurate” is misleading: even in that case, you’ve assumed a perfect fluid,
whereas in reality we think CDM satisfies the collision less Boltzmann equation.}
\\ \\Response: We stated that we also assumed the case of a pressureless perfect fluid.
\item Referee's suggestion: \textbf{I think the little f function is necessary, just combine (13) and (14).}
\\ \\Response: We think it will be more clear not to combine these two equations.
\\ \\Response: We stated that we also assumed the case of a pressureless perfect fluid.
\item Referee's suggestion: \textbf{isn’t A just basically normalizing the weights so that they integrate to unity?
Why not state that, it’s more physical.}
\\ \\Response: We stated that A is a normalization prefactor.
\item Referee's suggestion: \textbf{I suspect halos will make this worse. Basically you don’t account for biasing, but if the
biasing is not trivial then the optimal estimator is wrong.}
\\ \\Response: In our second paper, we will show that we can still get a good estimate with halo bias considered.
\\ \\

\textbf{Questions that I can't answer...}
\item As one of the applications, the authors mention the primordial
non-Gaussianity. The referee believes that primordial non-Gaussianity
deserves special attention here because its presence can potentially
change the estimator completely (by changing the nature of the
long-short correlation).
\item Also, there has been the idea of directly measuring large-scale modes using IM and then delensing—that should be cited.
\item \textbf{not sure if these two needs to be answered.} Is there a way to use kSZ velocities in concert with this? They offer constrains on large modes too an d wonder if there’s an optimal combination of them with short density modes.\\ \\ We do not expect any of these to be show-stoppers . . .” is just state with no justification. RSD really remove small-scale information from the field. Also not mentioned at all was baryonic effects, which Chisari + 2016 shows can change P(k) at k$\sim$0.4 by 5\%. If small scale info is being used optimally where the optimal weight just comes from the F2 kernel, well, this kernel does not include baryon physics, so these weights are no longer optimal in the presence of baryons. \textbf{We don't use modes up to k $\sim$ 0.4, isn't that right? But I'm not sure about the effect RSD would have.}
\item Why would confronting large-scale CMB anomalies with LSS help? Perhaps should be clarified. 
\item I think also adding forecasts of how much this reconstruction could improve relevant cosmological parameters would be good. “Successfully reconstructs” is subjective; quantifying how much additional information you get on X or Y cosmological parameter would be objective, and hence better.

\end{itemize}

\end{document}

### 2020-02-20 paper/response.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\newcommand\sd[1]{\emph{\bf [SD: #1]}}

\title{Response}
\author{Peikai Li, Scott Dodelson and Rupert A. C. Croft}
\date{}
\begin{document}

\maketitle
\noindent We sincerely thank the referees for their helpful comments and suggestions, which have significantly improved the manuscript.\\ \\
Following are the specific changes we have made:\\ \\
---------------------------------------------------------------------\\
Report of Referee A -- LK17288/Li\\
---------------------------------------------------------------------\\
\begin{itemize}
\item Referee's suggestion: \textbf{Although the paper shows solid analysis and demonstration with N-body
simulation and the method is relatively new, the small-scale
reconstruction has appeared in Physical Reviews in a couple of times:
for measuring gravitational waves (Masui \& Pen 2010, Jeong \&
Kamionkowski 2011, both PRL), for reconstructing the missing
long-wavelength mode for the 21cm surveys (Zhu, Pen+2015; 2016, both
PRD). All of the references mentioned above are missing in the paper.} \\ \\
Response: We cited all these papers.
\item Referee's suggestion: \textbf{In eq. (1)-(2), the authors use rather unconventional notation
$\times$ to represent the scalar product of two vectors.}
\\ \\Response: We fixed this error. 
\item Referee's suggestion: \textbf{Although the authors mention the 20\% bias on the right panel of Fig
2, showing summary statistics for the figure might be more helpful for
readers to understand the result.}
\\ \\Response: We also stated that the behavior of polar angle difference of the estimated and directly measured modes is worse in the second case. 
\item \textbf{There is a missing reference (shown as ??) on page 3.}\\ \\
Response: We fixed this error.\\
\item \textbf{As one of the applications, the authors mention the primordial
non-Gaussianity. The referee believes that primordial non-Gaussianity
deserves special attention here because its presence can potentially
change the estimator completely (by changing the nature of the
long-short correlation)}\\ \\
Response:  We agree that primordial non-Gaussianity can change the nature of the long-short correlations, and so could be constrained by comparing the indirectly inferred modes with directly measured large-scale modes, on scales where this can be done, (modulo the usual observational effects).\\

@@

\end{itemize} 
---------------------------------------------------------------------\\
Report of Referee B -- LK17288/Li\\
---------------------------------------------------------------------\\

\begin{itemize}
\item Referee's suggestion: \textbf{First sentence is too long—split}
\\ \\Response: This is similar to the comment from Referee A; please see our response there.
\item Referee's suggestion: \textbf{\\Should have citations for upcoming surveys;\\ Overall I think much more connection to the literature on density reconstruction needs to be made. e.g. work by Jens Jasche, work by Uros Seljak, Florent Leclercq, etc. \\}
\\ \\Response: Cited LSST and WFIRST as upcoming surveys and the papers referee has recommended.
\item Referee's suggestion: \textbf{\\1. An large-scale -$>$ a large-scale;\\2. Second-order perturbation of -$>$ contribution to; \\3. Along line of sight -$>$ missing the; \\4. Calculate its detectability -$>$ assess; \\ 5. Large parens in equation 2 around lhs; \\ 6. Need to define everything in (1)-(3): missing Phi, rho\_m, a, tau; \\7. define the Dirac delta distribution in the text
Also define what $<>$ means;\\ 8. Large parens in equation 8 last term;\\ 9. Say in words what you have done in equation 11—take the low-k mode outside the
expectation value; \\
10. I think the little f function is necessary, just combine (13) and (14); \\ 11. Below (14), explain more: you mean that the lhs of (13) has only short modes, but the
rhs shows sensitivity to long modes; \\ 12. Signal-to-noise needs dashes;\\ 13. In equation (19), if you would not have used the f function, you would find that the factor of 2 cancels out. And the weight is more understandable written as
$[F2*P_{lin}(ks) + F2*P_{lin}(ks’)]/P_{nl}*P_{nl}]$ because it’s basically dividing out nonlinearities
and then rescaling by a particular estimate of the nonlinearity;\\ 14. Bottom left page 3: Fig ?? Missing number in text;\\ 15. formatting at top of page 3 is not good; 16. “Larger than the matter radiation equality”—missing dash. Clearer would be “than the scale entering the horizon at matter-radiation equality”; \\17. Fig 2 caption is not ideal—please actually state what this Figure shows in the caption; \\18. An exciting next step”—that seems subjective. I think you should just say “is the logical next step”.}
\\ \\Response: We have improved these expressions according to the suggestions here.
\item Referee's suggestion: \textbf{Dash in Fourier-transformed}
\\ \\Response: We don't think it is necessary in our case. First of all, we don't think it will cause much confusion. Secondly, the definition of the quadratic estimator ( Eq(15) ) already had a hat on it. We feel that it will be redundant for it to have both "hat" and "dash".
\item Referee's suggestion: \textbf{“Completely accurate” is misleading: even in that case, you’ve assumed a perfect fluid,
whereas in reality we think CDM satisfies the collision less Boltzmann equation.}
\\ \\Response: We stated that we also assumed the case of a pressureless perfect fluid.
\item Referee's suggestion: \textbf{I think the little f function is necessary, just combine (13) and (14).}
\\ \\Response: We think it will be more clear not to combine these two equations.
\\ \\Response: We stated that we also assumed the case of a pressureless perfect fluid.
\item Referee's suggestion: \textbf{isn’t A just basically normalizing the weights so that they integrate to unity?
Why not state that, it’s more physical.}
\\ \\Response: We stated that A is a normalization prefactor.
\item Referee's suggestion: \textbf{I suspect halos will make this worse. Basically you don’t account for biasing, but if the
biasing is not trivial then the optimal estimator is wrong.}
\\ \\Response: In our second paper, we will show that we can still get a good estimate with halo bias considered.
\item Referee's suggestion: \textbf{Also, there has been the idea of directly measuring large-scale modes using IM and then delensing—that should be cited.}
\\ \\Response: We cited \url{https://arxiv.org/pdf/1908.08128.pdf}.
\item Referee's suggestion: \textbf{Is there a way to use kSZ velocities in concert with this? They offer constrains on large modes too an d wonder if there’s an optimal combination of them with short density modes.}
\\ \\Response: We agree that these could be another tracer of large-scale modes and it would be good for us to compare what we get from both methods. We cited a relevant paper \url{https://ui.adsabs.harvard.edu/abs/2009PhRvD..80f2003K/abstract}
\item Referee's suggestion: \textbf{We do not expect any of these to be show-stoppers ...” is just state with no justification. RSD really remove small-scale information from the field. Also not mentioned at all was baryonic effects, which Chisari + 2016 shows can change P(k) at k$\sim$0.4 by 5\%. If small scale info is being used optimally where the optimal weight just comes from the F2 kernel, well, this kernel does not include baryon physics, so these weights are no longer optimal in the presence of baryons.}
\\ \\Response: We don't think we need to consider baryonic effects at current stage because we only used $k$ modes up to $0.22 \, h \,\rm Mpc^{-1}$. We will consider RSD and potentially baryonic effects in our next work, when we apply this method to a light cone.
\item Referee's suggestion: \textbf{Why would confronting large-scale CMB anomalies with LSS help? Perhaps should be clarified.}
\\ \\Response: We clarified (in the paper) as follows: One physical mechanism that has been proposed as a possible explanation for the deficit in the large-angle CMBtemperature correlations is a suppression of primordial power on ~ Gpc scales. It would be very useful to verify if this new physics is also present in other probes of large-scale structure"  We also cited \url{https://ui.adsabs.harvard.edu/abs/2011JCAP...10..012H/abstract} in support of this.
\item Referee's suggestion: \textbf{I think also adding forecasts of how much this reconstruction could improve relevant cosmological parameters would be good. “Successfully reconstructs” is subjective; quantifying how much additional information you get on X or Y cosmological parameter would be objective, and hence better.}
\\ \\Response: We prefer to compute forecasts for cosmological parameters using our future work, which will include more realism, such as light cone effects, galaxy bias and redshift distortions, and it would be premature to do it here. We also included a quantitative comment that the current largest scale published measurement of the three dimensional power spectrum is for scale 0.02 h/Mpc, from \url{https://ui.adsabs.harvard.edu/abs/2018MNRAS.477.1604G/abstract}, and our figure 2 shows that it should be possible to make measurements using our method on scales of ~0.002 h/Mpc, which are ~10 times larger.

### 2020-02-20 paper/v2.tex
1

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\newcommand{\vs}{\nonumber\\}
\newcommand{\Var}{\rm Var}
\newcommand{\vk}{\vec{k}}
\newcommand{\ec}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\eec}[2]{Eqs.~(\ref{eq:#1}) and (\ref{eq:#2})}
\newcommand{\Ec}[1]{(\ref{eq:#1})}
\newcommand{\eql}[1]{\label{eq:#1}}
\newcommand{\rf}[1]{\ref{fig:#1}}
\newcommand{\sfig}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
%\newcommand{\sfigg}[2]{
%\includegraphics[width=0.424\paperwidth]{../plots/#1}
%        }
\newcommand{\sfigg}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
\newcommand{\sfiggg}[2]{
\includegraphics[width=0.4\paperwidth]{../plots/#1}
        }
\newcommand{\sfigr}[2]{
\includegraphics[angle=270,origin=c,width=#2]{#1}
        }
\newcommand{\sfigra}[2]{
\includegraphics[angle=90,origin=c,width=#2]{#1}
        }
\newcommand{\Sfig}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfig{../plots/#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}
\newcommand{\Sfigg}[2]{
   \begin{figure}[thbp]
    \sfigg{../plots/#1.pdf}{.8\paperwidth}
    \caption{{\small #2}}
    \label{fig:#1}
   \end{figure}
}
\newcommand{\Spng}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfigg{../plots/#1.png}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}

@@

\end{abstract}
\maketitle
\section{Introduction}
Measuring the distribution of matter on large scales is one of the goals of cosmological surveys \cite{LSST:2012ls}\cite{Wfirst:2012jg}. The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity. Direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered. Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average. This relation between long- and short-wavelength modes has been discussed in recent years \cite{Masui:2010prim}\cite{Baldauf:2011fer}\cite{Jeong:2012foss}\cite{Jasche:2013bay}\cite{Leclercq:2013remp}\cite{Li:2014ssc}\cite{Zhu:2016tidal}\cite{Barreira:2017res}\cite{Seljak:2017opt}\cite{Akitsu:2018dist}\cite{Foreman:2018line}\cite{Zhu:2018cm}. The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully achieve this goal, here we construct a quadratic estimator to measure long-wavelength modes indirectly.

@@

\noindent{\it Quadratic Estimator.}\label{sec2}
We can now construct the quadratic estimator for long-wavelength modes starting from \ec{2pt} and summing over as many pairs as possible with weights that maximize the signal-to-noise. As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest},
\end{eqnarray} 
with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ \peikai{is the normalization prefactor} defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1} \eql{a}
\end{eqnarray}
In the absence of shot noise the Gaussian noise is given by:
\be 
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)*}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
\ee 
with 
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
&&g(\vec{k}_{s},\vec{k}_{s}')
=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs
&=&\frac{F_2(-\vec{k}_s,\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s)+F_2(-\vec{k}_s',\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s')}{P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs 
\end{eqnarray} 
The noise term reduces simply to $N(\vk_l)=A(\vk_l)$. We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$.

Assuming Gaussian noise, the projected detectability of a $P(k_l)$ measurement using the quadratic estimator can be expressed as:
\be
\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error},
\ee
where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
In Fig.~\rf{SN}, we show the projected errors on the long-wavelength power spectrum using this quadratic estimator in a large survey. The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$. We will see that this choice of the upper limit is reasonable for our current construction at $z=0$. Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$).

@@

Another way of examining the success of the quadratic estimator is to transform the estimated density field back to real space to form $\hat\delta(\vec x)$ and then compare with the actual large scale density field $\delta(\vec x)$ in the simulation. The 7 panels in the top two rows of Fig.~\rf{real1} compare these two fields; each panel is a slice of the full simulations. The bottom panel shows the difference between the estimated and true density fields. It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.
\section{Conclusion}\label{sec4}
In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly. The estimator works well on an N-Body simulation, so applying this estimator to survey data is \peikai{the logical} next step. Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions \cite{Kaiser:1987rsd}, and light-cone effects. We do not expect any of these to be show-stoppers, so it is tempting to speculate about the possibilities that will open up with this estimate of the large scale density field. 
First, we can hope to measure 3D clustering on scales larger than the scale entering the horizon at matter-radiation equality without worrying about large-scale systematic effects. General relativistic effects are strongest on large scales (e.g., \cite{Jeong:2012ls}), and these could be detected. There is evidence of large scale anomalies, in the CMB, that could be confronted with maps of large scale structure obtained with this estimator. Primordial non-Gaussianity generated by inflation leaves an imprint on the largest scales. There is even the possibility of cross-correlating the large-scale matter field with the CMB itself to extract information about the longest wavelength modes in the universe. Since the current epoch of acceleration is a large-scale, late-time effect, there is the possibility of learning about the mechanism responsible for acceleration. Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory.\\
\acknowledgements
We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu. The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).

>>>>

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\newcommand{\vs}{\nonumber\\}
\newcommand{\Var}{\rm Var}
\newcommand{\vk}{\vec{k}}
\newcommand{\ec}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\eec}[2]{Eqs.~(\ref{eq:#1}) and (\ref{eq:#2})}
\newcommand{\Ec}[1]{(\ref{eq:#1})}
\newcommand{\eql}[1]{\label{eq:#1}}
\newcommand{\rf}[1]{\ref{fig:#1}}
\newcommand{\sfig}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
%\newcommand{\sfigg}[2]{
%\includegraphics[width=0.424\paperwidth]{../plots/#1}
%        }
\newcommand{\sfigg}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
\newcommand{\sfiggg}[2]{
\includegraphics[width=0.8\paperwidth]{../plots/#1}
        }
\newcommand{\sfigr}[2]{
\includegraphics[angle=270,origin=c,width=#2]{#1}
        }
\newcommand{\sfigra}[2]{
\includegraphics[angle=90,origin=c,width=#2]{#1}
        }
\newcommand{\Sfig}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfig{../plots/#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}
\newcommand{\Sfigg}[2]{
   \begin{figure}[thbp]
    \sfiggg{../plots/#1.pdf}{.8\paperwidth}
    \caption{{\small #2}}
    \label{fig:#1}
   \end{figure}
}
\newcommand{\Spng}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfigg{../plots/#1.png}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}

@@

\end{abstract}
\maketitle
\section{Introduction}
Measuring the distribution of matter on large scales is one of the goals of cosmological surveys \cite{LSST:2012ls}\cite{Wfirst:2012jg}. The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity. \peikai{In \cite{Karkare:2019delen}, a method of using delensing with intensity mapping has been proposed to directly measure large scale modes.} But generally speaking, direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered. \peikai{As pointed out by \cite{Modi:2019hydr}, 21cm intensity mapping is one area where due to foregrounds, large-scale (line of sight) modes will be impossible to measure directly.}

Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average. This relation between long- and short-wavelength modes has been discussed in recent years \cite{Masui:2010prim}\cite{Baldauf:2011fer}\cite{Jeong:2012foss}\cite{Jasche:2013bay}\cite{Leclercq:2013remp}\cite{Li:2014ssc}\cite{Zhu:2016tidal}\cite{Barreira:2017res}\cite{Seljak:2017opt}\cite{Akitsu:2018dist}\cite{Foreman:2018line}\cite{Zhu:2018cm}. The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully achieve this goal, here we construct a quadratic estimator to measure long-wavelength modes indirectly.

@@

\section{Quadratic Estimator}\label{sec2}
We can now construct the quadratic estimator for long-wavelength modes starting from \ec{2pt} and summing over as many pairs as possible with weights that maximize the signal-to-noise. As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest},
\end{eqnarray} 
with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ \peikai{is the normalization prefactor} defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1} \eql{a}
\end{eqnarray}
In the absence of shot noise the Gaussian noise is given by:
\be 
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)*}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
\ee 
with 
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
&&g(\vec{k}_{s},\vec{k}_{s}')
=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs
&=&\frac{F_2(-\vec{k}_s,\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s)+F_2(-\vec{k}_s',\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s')}{P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs 
\end{eqnarray} 
The noise term reduces simply to $N(\vk_l)=A(\vk_l)$. We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$.

Assuming Gaussian noise, the projected detectability of a $P(k_l)$ measurement using the quadratic estimator can be expressed as:
\be
\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error},
\ee
where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
In Fig.~\rf{SN}, we show the projected errors on the long-wavelength power spectrum using this quadratic estimator in a large survey. \peikai{The current largest scale published measurement of the three dimensional power spectrum is for scale $0.02 \, h \,\rm Mpc^{-1}$, from \cite{Gil-Marin:2018SDSS}. And our Fig.~\rf{SN} shows that it should be possible to make measurements using our method on scales of $0.002 \, h \,\rm Mpc^{-1}$, which are $\sim$10 times larger.} The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$. We will see that this choice of the upper limit is reasonable for our current construction at $z=0$. Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$).

@@

Another way of examining the success of the quadratic estimator is to transform the estimated density field back to real space to form $\hat\delta(\vec x)$ and then compare with the actual large scale density field $\delta(\vec x)$ in the simulation. The 7 panels in the top two rows of Fig.~\rf{real1} compare these two fields; each panel is a slice of the full simulations. The bottom panel shows the difference between the estimated and true density fields. It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.
\section{Conclusion}\label{sec4}
In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly. \peikai{Similarly to this construction, kSZ velocities \cite{Kosowsky:2009ksz} might also be a good tracer of large-scale modes. We can take the advantage of it's small scale information and potentially get a better constraint of large-scale modes. We will leave this part to future work.}

The estimator works well on an N-Body simulation, so applying this estimator to survey data is \peikai{the logical} next step. Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions \cite{Kaiser:1987rsd}, and light-cone effects. We do not expect any of these to be show-stoppers, so it is tempting to speculate about the possibilities that will open up with this estimate of the large scale density field. 
First, we can hope to measure 3D clustering on scales larger than the scale entering the horizon at matter-radiation equality without worrying about large-scale systematic effects. General relativistic effects are strongest on large scales (e.g., \cite{Jeong:2012ls}), and these could be detected. There is evidence of large scale anomalies, in the CMB, that could be confronted with maps of large scale structure obtained with this estimator. \peikai{One physical mechanism that has been proposed as a possible explanation for the deficit in the large-angle CMB temperature correlations is a suppression of primordial power on $\sim$ Gpc scales \cite{Hearin:2011anom}. It would be very useful to verify if this new physics is also present in other probes of large-scale structure.} Primordial non-Gaussianity generated by inflation leaves an imprint on the largest scales. There is even the possibility of cross-correlating the large-scale matter field with the CMB itself to extract information about the longest wavelength modes in the universe. Since the current epoch of acceleration is a large-scale, late-time effect, there is the possibility of learning about the mechanism responsible for acceleration. Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory.\\
\acknowledgements
We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu. The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
